\documentclass{article}
%\usepackage[a4paper, total={6in, 9in}]{geometry}
\usepackage{tabularx}
\usepackage{booktabs}

\title{SE 3XA3: Problem Statement\\Wordle 2.0}

\author{Team \#08
		\\ Richard Fan, fanr13
		\\ Noel Zacharia, zacharin
		\\ Biranugan Pirabaharan, pirabahb
}

\date{January 27, 2022}

\begin{document}

\maketitle

\newpage

\tableofcontents
\listoftables

\newpage

\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
Jan/27/2022 & Biranugan, Richard, Noel & Initial Draft\\
\bottomrule
\end{tabularx}
\end{table}

\newpage

\section{Introduction}\label{sec:intro}
Puzzle games have been around for a long time. Wordle is one such game that allows players to test their knowledge of words while having fun at the same time. Being web-based, this game is easily accessible by many people. The intuitive gameplay allows players to quickly learn all the rules while being challenged by the puzzle at the same time. This unique combination gives Wordle its appeal and has captured many players around the world. We wish to preserve Wordle’s charm while also improving the experience by implementing new gameplay features, improving the user interface, and introducing replay value.

\section{Context}\label{sec:con}

The main stakeholders for our game are the end-users, the clients and the developers. The end-users will be the players. Since the game is so easy to learn and play we expect our players will range from children who are just learning new words to avid gamers who play all sorts of games. The players also dictate our game’s environment, since the game can be run on any web browser it is accessible to almost everyone and playable on most systems. Our clients are the TAs and the course instructor, they assigned us the task of making a project and thus have a say in how the game will turn out. They also have given us deadlines for certain milestones of the game and have decided how much time we have for development and implementation. Finally, the developers are us. We dictate what is included in the final product which we will base completely on how much we can accomplish and what will produce the best game for the players.

\section{Importance}\label{sec:import}

Wordle is a popular game that has taken the world by storm. However, this game does not provide users with a good graphical UI, it does not have a dark mode and the repo we are recreating this app from does not have proper test cases. These are important issues that we wish to address in order to provide users with a seamless graphical experience and minimize sources of errors by having a proper test plan and test cases implemented.


\end{document}